`r paste0('# ', prov_short_name, '{data-navmenu="',stp_short_name,'"}')`

```{r setup, include=FALSE}

admitted_projections <- cp %>% 
  filter(wait_type == 'DTA_Wait') %>% 
  select(tfc_name, 
         current_ptl,
         current_long_waits,
         est_position_at_deadline,
         mean_change_lw,
         change_trend) %>% 
  arrange(desc(est_position_at_deadline))

op_projections <- cp %>% 
  filter(wait_type == 'OP_Wait')%>% 
  select(tfc_name,
         current_ptl,
         current_long_waits,
         est_position_at_deadline,
         mean_change_lw,
         change_trend) %>% 
  arrange(desc(est_position_at_deadline))

total_dta_specs <-  spo %>% 
  filter(wait_type=='DTA_Wait') %>% 
  pull(total_specs)

total_op_specs <-  spo %>% 
    filter(wait_type=='OP_Wait') %>% 
  pull(total_specs)

dta_breach_specs <- nrow(admitted_projections)
op_breach_specs <- nrow(op_projections)

```


Column {data-width=425}
-----------------------------------------------------------------------

### `r paste0(prov_short_name, ' Admitted specialities - projected breaches')`

```{r admitted-projections}

fn_projections_dt(admitted_projections)

```

### `r paste0(prov_short_name, ' Non-Admitted specialities - projected breaches')`

```{r outpatient-projections}

fn_projections_dt(op_projections)

```

Column {data-width=425}
-----------------------------------------------------------------------

### `r paste0(prov_short_name, ' Admitted long waits trend by week')` 

``` {r apc-trend}

apc_lw_trend<- fn_lw_trend(flwd,'DTA_Wait')

ggplotly(apc_lw_trend)


```

### `r paste0(prov_short_name, ' Outpatient long waits trend by week')`

``` {r op-trend}
op_lw_trend<- fn_lw_trend(flwd,'OP_Wait')

ggplotly(op_lw_trend)
```

Column {data-width=150}
-----------------------------------------------------------------------
### `r paste0(prov_short_name, ' Number of admitted specialities with projected long waits after deadline')`

```{r valuebox-admitted}

valueBox(dta_breach_specs, icon = 'fa-calculator')

```

### `r paste0(prov_short_name, ' Percentage of admitted specialities with projected long waits after deadline')`
```{r valuebox-admitted}

valueBox(round(dta_breach_specs/total_dta_specs*100,1), icon = 'fa-percent')

```

### `r paste0(prov_short_name, ' Number of non-admitted specialities with projected long waits after deadline')`

```{r valuebox-nonadmitted}

valueBox(op_breach_specs, icon = 'fa-calculator')

```

### `r paste0(prov_short_name, ' Percentage of non-admitted specialities with projected long waits after deadline')`

```{r valuebox-nonadmitted}

valueBox(round(op_breach_specs/total_op_specs*100,1), icon = 'fa-percent')

```